The first high-redshift Changing Look Quasars

### 2019-11-04 tex/CIV_CLQs.tex
tex/CIV_CLQ Acknowledgement update
CIV_CLQs key update

  \begin{tabu}{l ll  lccc c r }

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. Note the REW logarithmic scaling.}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn} = \sqrt{ R^{3}/GM} \rightarrow  t_{\rm dyn}  \sim M^{2}$
if e.g. $R_{\rm Sch}= 2GM /c^{2}$.
%and $t_{\rm dyn} =\sqrt{ R^{3}/GM}$ means e.g $t_{\rm dyn} \sim 6 G^{3} M^{3} / GM c^{2} \sim 6G^{2} M^{2} / c^{2}.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.7cm, trim=0.2cm 0.2cm 0.2cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_LBol_20191015.png}
   \vspace{-12pt}
   \caption[]{The Baldwin Plot. The bolometric luminosities are from \citet{Kozlowski2017},
     while the REW measurements are from \citet{Hamann2017}.}
  \label{fig:CIV_Baldwin}
\end{figure}

@@

EHT2017 data includes tracks from four separate
days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{(EHT_PaperIV} timescale is short
compared to the decorrelation timescale of simulated images, which is
$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
plasma.

From \citet{EHT_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
\begin{equation}
R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
\end{equation}
giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
%\begin{equation}
%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
%\end{equation}
%and a {\it dynamical timescale}, $t_{\rm dyn}$
%\begin{equation}
%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
% \end{equation}
%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.

@@

\noindent
We thank:
\begin{list}{$\circ$}{}  
  \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion. 
\end{list}

>>>>

  \begin{tabu}{l ll  ll cc c r }

@@

\begin{table}
  \begin{centering}
    \begin{tabular}{c c l l}
      \hline
      \hline
      Object             & MJD      & Cont. Lumin        &  Cont. slope \\
      \hline
                             & 53498   &  40040$\pm$34  & -1.656$\pm$ 0.006 \\
      J1205+3422    & 58538   &   ---                   &  ---     \\
                             & 58693   &   ---                    &  ---     \\
                             &              &                             & \\
                             & 54553   &  3774$\pm$111   &  -1.472$\pm$0.197   \\
      J1638+2827    & 55832  &  2433$\pm$14     &  -2.316$\pm$0.051  \\  
                             & 58583   &  3292$\pm$9       &    -0.541$\pm$0.010 \\
                             &              &                             &\\
                            & 56189    &  ---                      &  ---     \\
    J2228+2201     & 56960   &  7889$\pm$14      &  -1.729$\pm$0.015     \\
                            & 58693   &  ---                       &  ---     \\
    \hline
    \hline
  \end{tabular}
  \caption{Quasar continuum $\nu L_{\nu}$ luminosities and slopes, at
the fixed rest-frame wavelengths 1450\AA\ from QSFIT.  The
luminosities are in units of 10$^{42}$~erg~s$^{-1}$.}
  \label{tab:Baldwin}
  \end{centering}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4   SECTION 4  
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_REWvsFWHM_20191029.png}
   \vspace{-12pt}
  \caption[]{The Rest Equivalent Width (REW) vs. Full Width Half Maximum (FWHM) 
of the \civ\ emission line in the BOSS DR12 quasar sample using the catalogue 
of \citet{Hamann2017}. %Note the REW logarithmic scaling.
}
  \label{fig:REWvsFWHM}
\end{figure}

@@

\subsection{The Baldwin Effect}
The variable properties of the rest-frame UV quasar emission lines
have been long studied, with the global (or ensemble) Baldwin Effect
(the anti-correlation between the EW of the emission line and the
underlying continuum luminosity of single-epoch observations of a
large number of AGN, first noted in \citet{Baldwin1977}.  More
recently, the intrinsic Baldwin effect, the same anti-correlation but
in an individual, variable AGN.  The variable properties of high-$z$
quasars, however, has been less well studied. Reasons for this include
more massive systems will tend to have longer timescales with e.g.
$t_{\rm dyn}  \sim M^{2}$ if $t_{\rm dyn} = \sqrt{ R^{3}/GM}$ and $R_{\rm Sch}= 2GM /c^{2}$.

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm, trim=0.2cm 0.2cm 0.0cm 0.2cm, clip]
  {figures/CIV_CLQs_Baldwin_20191104v3.png}
   \vspace{-12pt}
   \caption[]{The \civ\ Equivalent width and the underlying continuum luminosity,
     commonly referred to as The Baldwin Plot. The continuum luminosities are
     from \citet{Kozlowski2017},
     the REW measurements are Table~\ref{tab:Baldwin}.}
  \label{fig:CIV_Baldwin}
\end{figure}

@@

EHT2017 data includes tracks from four separate
days of observing,;each day is 2.8$r_{g}$ $c^{-1}$ \citep{EHT2019_PaperIV} timescale is short
compared to the decorrelation timescale of simulated images, which is
$\sim$50 $r_{g}$ $c^{-1}$, and smaller than the light-crossing time of the source
plasma.

From \citet{EHT2019_PaperI}, $M_{M87^{*}} = (6.5\pm0.7) \; \times \; 10^{9}$ $M_{\odot}$, 
\begin{equation}
R_{s} = 2 r_{g} =  2 GM/c^{2}  = 9.598 \times10^{12} {\rm m}.
\end{equation}
giving a {\it light crossing timescale} of $t_{\rm lt} = R_{s} / c = 32 015 {\rm secs}$ (0.37 days).
%\begin{equation}
%t_{\rm lt} = R_{s} / c = 32015 {\rm secs}$
%\end{equation}
%and a {\it dynamical timescale}, $t_{\rm dyn}$
%\begin{equation}
%$t_{\rm dyn}  =  sqrt{ R_{s}^{3}/G M}
% \end{equation}
%also (!!!!!) of $t_{\rm dyn}  =  \sqrt{ R_{s}^{3}/G M}$ = 32015 seconds.

@@

\noindent
We thank:
\begin{list}{$\circ$}{}
  \item  Dr. Giorgio Calderone for discussions to the utility of the QSFit routine and line measurements. 
  \item Andy Lawrence, Mike Hawkins and David Homan for useful discussion.
\end{list}
